Stemmer Tool Manual

### 2012-08-27 trunk/tex/Manual.tex
updated Manual

\section{Build the Tool}
\subsection{Dependencies}
In order to be able to build and run Sarf, the following dependencies must be installed:
\begin{itemize}
\item mysql-client
\item mysql-server
\item libmysqlcppconn
\item libmysqlcppconn-dev
%\item subversion
\item qt-sdk
%\item qtcreator
\item g++
%\item graphviz
\end{itemize}
The above tools can be downloaded and installed using the ``Synaptic Package Manager'' in ubuntu systems or through the ``apt-get'' command. You can use similar commands such as yum in other linux distributions.
\subsubsection{datrie}
You also need to download the double-array trie library called ``datrie''. Datrie can be downloaded from the following link:\\
\url{http://linux.thai.net/~thep/datrie/datrie.html#Download }\\
After downloading the trie structure to a destination you specify, go to {\bf datrie/libdatrie-0.2.3} and apply the following commands to configure and build.
\begin{enumerate}
\item ./configure
\item make
\end{enumerate}
Note that the name of the folder ``libdatrie-0.2.3'' includes the version of the library downloaded. So you could have a number in your download referring to a different version, which shouldn't cause any problem.

@@

Given that you put the datrie file in the same directory as the root folder ``ATSarf'', you can set the link to it as follows:
\begin{verbatim}
ln -s ../datrie/libdatrie-0.2.3/ datrie
\end{verbatim}

>>>>

\section{Build the Tool}
\subsection{Dependencies}
In order to be able to build and run Sarf, the following dependencies must be installed:
\begin{itemize}
\item mysql-client
\item mysql-server
\item libmysqlcppconn
\item libmysqlcppconn-dev
%\item libqjson-dev
%\item subversion
\item qt-sdk
%\item qtcreator
\item g++
%\item graphviz
\end{itemize}
The above tools can be downloaded and installed using the ``Synaptic Package Manager'' in ubuntu systems or through the ``apt-get'' command. You can use similar commands such as yum in other linux distributions.
\subsubsection{datrie}
You also need to download the double-array trie library called ``datrie''. Datrie can be downloaded from the following link:\\
\url{http://linux.thai.net/~thep/datrie/datrie.html#Download }\\
After downloading the trie structure to a destination you specify, go to {\bf datrie/libdatrie-0.2.3} and apply the following commands to configure and build.
\begin{enumerate}
\item ./configure
\item make
\end{enumerate}
Note that the name of the folder ``libdatrie-0.2.3'' includes the version of the library downloaded. So you could have a number in your download referring to a different version, which shouldn't cause any problem.

\subsubsection{QJson}
QJson is a qt-based library that maps JSON data to QVariant objects: JSON arrays will be mapped to QVariantList instances, while JSON objects will be mapped to QVariantMap. This library can be downloaded from the following link:\\
\url{http://sourceforge.net/projects/qjson/files/}\\
After downloading QJson to the desired destination, follow the instructions found in the ``INSTALL'' file found in the root directory ``qjson'' to install the library.

@@

Given that you put the datrie file in the same directory as the root folder ``ATSarf'' and you are in the ``third'' directory, you can set the link to it as follows:
\begin{verbatim}
ln -s ../../datrie/libdatrie-0.2.3/ datrie
\end{verbatim}

Similarly, given that you add the QJson library to the same directory as the root folder ``ATSarf'', add a link to it using the following command:
\begin{verbatim}
ln -s ../../qjson/ qjson
\end{verbatim}
